Bacterial Microbiome and Obesity Meta-analysis Supplemental

### 2016-06-22 results/tables/table_1.Rmd
Ignore NAs when calculating percent obese
Fix Schubert entry in Table 1

region <- c(
	baxter = "V4",
	escobar = "V2",
	hmp = "V3-V5",
	ross = "V1-V3",
	schubert = "V4",
	turnbaugh = "V2",
	wu = "V1-V2",
	zupancic = "V3-V5",
	goodrich = "V4",
	zeevi = "V3-V4"
)

technology <-  c(
	baxter = "MiSeq",
	escobar = "454",
	hmp = "454",
	ross = "454",
	schubert = "MiSeq",
	turnbaugh = "454",
	wu = "454",
	zupancic = "454",
	goodrich = "MiSeq",
	zeevi = "MiSeq"
)

@@

	per_obese <- format(round(100 * mean(metadata$obese), 1), nsmall=1L)

>>>>

region <- c(
	baxter = "V4",
	escobar = "V2",
	hmp = "V3-V5",
	ross = "V1-V3",
	schubert = "V3-V5",
	turnbaugh = "V2",
	wu = "V1-V2",
	zupancic = "V3-V5",
	goodrich = "V4",
	zeevi = "V3-V4"
)

technology <-  c(
	baxter = "MiSeq",
	escobar = "454",
	hmp = "454",
	ross = "454",
	schubert = "454",
	turnbaugh = "454",
	wu = "454",
	zupancic = "454",
	goodrich = "MiSeq",
	zeevi = "MiSeq"
)

@@

	per_obese <- format(round(100 * mean(metadata$obese, na.rm=T), 1), nsmall=1L)
